A preliminary constraint grammar for Russian

### 2015-03-25 2015-nodalida-ruscg/ruscg.tex
a small amount of text about the corpus
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@59512 72bbbca6-d526-0410-a7d9-f06f51895060

\emph{Morphosyntactically congruent} ambiguity occurs between homographs 
that belong to separate lexemes, and whose morphosyntactic values are identical, 
as shown in \ref{ex:MScongruent}. As indicated in Table~\ref{table:ambiguity}, 
this kind of ambiguity is relatively rare, and resolving this ambiguity requires 
the use of technologies such as Word Sense Disambiguation.

@@

>>>>

\emph{Morphosyntactically congruent} ambiguity occurs between homographs 
that belong to separate lexemes, and whose morphosyntactic values are identical, 
as shown in \ref{ex:MScongruent}. As indicated in Table~\ref{table:ambiguity}, 
this kind of ambiguity is relatively rare, and resolving this ambiguity requires 
the use of technologies such as word sense disambiguation.

@@

\subsection{Corpus}

In order to evaluate the grammar we hand-annotated 10,150 words of Russian text
from Wikipedia articles, public domain literature and freely-available news sources. The
annotated texts are available online under the {\sc cc-by-sa} licence.\footnote{\url{...}}

Hand-annotation proceeded as follows: The text was first morphologically analysed, 
and then an annotator read through the output of the morphological analyser, commenting
out the readings which were not appropriate in context. This annotated text was then checked
by a second annotator.

We chose our own texts as opposed to using a well-known hand-annotated corpus
such as the Russian National Corpus (RNC) for two main reasons: the first was that the 
RNC is not freely available; the second was that the standards for tokenisation, part-of-speech
and morphological description are different from our morphological analyser.
